---
title: "Introduction to R package StatComp20015"
author: "20015"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to R package StatComp20015}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Overview

__StatComp20015__ is a simple R package developed to simulate the processes of _SI models_, _SIS models_ and _SIR models_, and contains several functions related to them. Given an initial value,the function can return to: _infe_:Percentage of people infected per day; _susc_:Percentage of susceptible persons per day; _reco_:Percentage of people recovering or dying per day; _I_:The total number of people infected; _S_:The total number of people susceptible; _R_:The total number of people who recover or die and so on.

__StatComp20015__ also save all my homework.

R package 'deSolve' is used to solve an ordinary differential equation.

## SI model

The source R code for _si_ is as follows:
```{r,eval=FALSE}
library(deSolve)
si <- function(i0,beta,t_range,N=1e4){
  devi <- function(t,i,parms) list(beta * i *(1-i))
  infe <- ode(y = i0, times = t_range, func = devi, parms = NULL)
  susc <- cbind(t_range,1-infe[,2])
  I <- cbind(t_range,infe[,2]*N)
  S <- cbind(t_range,susc[,2]*N)
  if(infe[length(t_range),2]==1) in.time <- infe[infe[,2]>=1,][1,1] else 
    in.time <-'The time step is too short'
  return(list(infe=infe, susc=susc, I=I, S=S, in.time=in.time))
}
```
Example:
```{r,eval=FALSE}
SI <- si(i0=1e-4,beta=1.2,t_range=seq(0,100,1))
plot(SI$infe,type='l',col='red',xlab = 'time' , ylab='percentage',main='SI model')
lines(SI$susc,type='l',col='blue')
legend('right',c('infective percentage','susceptible percentage'),col=c('red','blue'),lty=c(1,1))
```

## SIR model

The source R code for _sir_ is as follows:
```{r,eval=FALSE}
library(deSolve)
sir <- function(i0,r0,beta,gam,t_range=seq(0,100,1)){
  s0 <- 1-i0-r0
  devr <- function(t,r,parms) list(gam*(1-r-s0*exp(-beta*r/gam)))
  reco <- ode(y = r0, times = t_range, func = derivs_r, parms = NULL)
  s <- s0*exp(-beta*reco[,2]/gam)
  susc <- cbind(t_range,s0*exp(-beta*reco[,2]/gam))
  infe <- cbind(t_range,pmax(1-susc[,2]-reco[,2],0))
  t.peak <- infe[which.max(infe[,2]),1]  
  if(infe[length(t_range),2]<1e-8) t.stop <- infe[infe[,2]<1e-8,][1,1] else 
    t.stop <-'The time step is too short'
  return(list(infe=infe, susc=susc, reco=reco,t.peak=t.peak,t.stop=t.stop))
}
```
Example:
```{r,eval=FALSE}
SIR <- sir(i0=0.01,r0=0,beta=1.2,gam=0.4,t_range=seq(0,100,1))
plot(SIR$infe,type='l',col='red',xlab = 'time' , ylab='percentage',main='SIR model')
lines(SIR$susc,type='l',col='blue')
lines(SIR$reco,type='l',col='green')
legend('right',c('infective percentage','susceptible percentage','recovery percentage'),col=c('red','blue','green'),lty=c(1,1,1))
```

## SIS model

The source R code for _sis_ is as follows:
```{r,eval=FALSE}
library(deSolve)
sis <- function(i0,beta,gam,t_range=seq(0,100,1)){
  s0 <- 1-i0
  devi <- function(t,i,parms) list((beta-gam-beta*i)*i)
  infe <- ode(y = i0, times = t_range, func = devi, parms = NULL)
  susc <- cbind(t_range,1-infe[,2])

  if(infe[length(t_range),2]-infe[length(t_range)-1,2]==0){
    t.stable <- infe[infe[length(t_range),2]-infe[,2]<1e-6,][1,1]
    per.stable <- infe[t.stable,2]
  } else {
    t.stable <-'The time step is too short'
    per.stable <-'The time step is too short'
  }
  return(list(infe=infe, susc=susc,t.stable=t.stable,per.stable=per.stable))
}
```
Example:
```{r,eval=FALSE}
SIS <- sis(i0=0.01,beta=1.2,gam=0.4,t_range=seq(0,100,1))
plot(SIS$infe,type='l',col='red',xlab = 'time' , ylab='percentage',main='SIS model')
lines(SIS$susc,type='l',col='blue')
legend('right',c('infective percentage','susceptible percentage'),col=c('red','blue'),lty=c(1,1))
#' 
```


